\documentclass[11pt,letterpaper,sans]{moderncv}

%%%%%%%%%%
% Themes %
%%%%%%%%%%

\moderncvstyle{banking}
\moderncvcolor{orange}


%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%

\usepackage[top=0.5in, left=0.75in, right=0.75in, bottom=0.5in]{geometry}
\usepackage{etoolbox}


%%%%%%%%%%
% Macros %
%%%%%%%%%%

% Usage:
% \begin{pzentry}{title}{subtitle}{date}
% description
% \end{pzentry}
\newenvironment{pzentry}[3]
{\textbf{#1}\notblank{#2}{\textit{~- #2}}{}\hfill\textit{#3}\\\normalsize}
{\bigskip}


%%%%%%%%%%%%%%%%%
% Personal data %
%%%%%%%%%%%%%%%%%

% \firstname{Peter}
% \lastname{Zieske}
\name{Peter}{Zieske}
% \address{7319 Willow Creek Drive}{Ypsilanti, MI 48197}
% \mobile{+1~(734)~358~7208}
\email{pzieske@live.com}
% \email{pdz8@cornell.edu}
\homepage{peterzieske.com}
\social[linkedin]{peter-zieske}
\social[github]{pdz8}


%%%%%%%%%%
% Resume %
%%%%%%%%%%

\begin{document}

\makecvtitle

%%%%%%%%%%%%%%%%%%%%%
\section{Education} %
%%%%%%%%%%%%%%%%%%%%%

\begin{pzentry}{Cornell University}{M.Eng., Computer Science}{Aug 2014 - May 2015}
Cumulative GPA: 4.052
\end{pzentry}

\begin{pzentry}{Cornell University}{B.S., Computer Science}{Aug 2011 - May 2014}
Cumulative GPA: 3.876
\end{pzentry}

% \cventry{Sept 2007 - May 2011}{\upshape GPA: $\sim$ 4.2}
% {Lincoln Senior High School}{Ypsilanti, MI}
% {}
% {}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience} %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{pzentry}{Microsoft}{SDE}{Sept 2015 - Present}
Working within Engineering Systems of Operating Systems Core group.
[C\#, C/C++]
\end{pzentry}

\begin{pzentry}{Microsoft}{SDE Intern}{May 2014 - Aug 2014}
% Worked to enhance security and flexibility in Engineering Systems of Operating Systems Core.
Worked within Engineering Systems of Operating Systems Core.
Built from scratch a Windows SSH server compatible with both OpenSSH and PuTTY clients.
[C/C++]
\end{pzentry}

\begin{pzentry}{Cornell University}{Teaching Assistant}{Aug 2013 - May 2015}
Served on course staff for CS 3110 Data Structures and Functional Programming, CS 4820 Introduction to the Analysis of Algorithms ($\times$2), and CS 4410/4411 Operating Systems.
[OCaml, \LaTeX, Python, C, Bash]
\end{pzentry}

\begin{pzentry}{Microsoft}{SDET Intern}{May 2013 - Aug 2013}
Developed both traditional and randomized testing automation for the Email and Calendar team in Windows Phone.
[C\#]
\end{pzentry}


%%%%%%%%%%%%%%%%%%%%
\section{Projects} %
%%%%%%%%%%%%%%%%%%%%

\begin{pzentry}{CrowdVerity}{}{Jan 2015 - May 2015}
Worked with professor Emin G\"{u}n Sirer on M.Eng project \href{http://crowdverity.com/}{crowdverity.com}.
CrowdVerity imports facts from the real-world into the digital and blockchain domains.
[Ethereum, Django, HTML/JavaScript/CSS]
\end{pzentry}

\begin{pzentry}{PORTCULLIS}{}{Jan 2015 - May 2015}
Built a secure password manager in a team of 4.
PORTCULLIS featured 2-factor authentication, sharing/revocation, and an almost trustless central server.
[Java]
\end{pzentry}

\begin{pzentry}{Pirates of the Stratosphere}{}{May 2013 - Aug 2013}
Worked in a 5 member interdisciplinary team to create a pirate-themed shooter.
The game won in Cornell's 2013 GDIAC Showcase.
[C\#]
\end{pzentry}

% \cventry{Jan 2013 - May 2013}{Undergraduate Researcher}
% {Cornell University}{Ithaca, NY}
% {}
% {Explored the use of network flow algorithms in computer vision under Professor Ramin Zabih.}
% \medskip

\begin{pzentry}{Violet Nano-Satellite Project Team}{}{Sept 2011 - May 2013}
Worked with the satellite's power board within the team's Command and Data Handling subsystem.
[C, Python]
\end{pzentry}

\begin{pzentry}{Windows Phone App Development}{}{June 2012 - Aug 2013}
Designed and developed 5 apps for Windows Phone 7 and 8 with total downloads exceeding 10k.
The app \emph{Bus Alarm} placed first in Microsoft's 2013 Intern AppHack competition.
[C\#]
\end{pzentry}


% \cventry{June 2012 - August 2012}{Developer}
% {Mt. Olivet Cemetery Database}{Chelsea, MI}
% {}
% {Create a user-friendly management system for a cemetery near my hometown. [VBA]}
% \medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Technical Skills} %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvitem{Languages}{C\#, C/C++, Java, OCaml, Python, HTML/JavaScript/CSS, VBA, Matlab, Prolog, Perl}
% \medskip
% \cvitem{Tools}{\LaTeX, Git, Powershell, Unix, Visual Studio, Django, AngularJS}

\end{document}
